\Title

### 2020-03-26 manuscript/manuscript.tex
Remove rubbish line from manuscript
Improve manuscript

The fundamental solution of any harmonic field can be obtained as follows
\citep{blakely1995}:

@@

Worth noting that solving equations~\ref{eq:linear-problem-g}
and~\ref{eq:linear-problem} is equivalent to performing an inversion and thus
solving an ill-posed problem by nature due to the non-uniqueness and the
instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions \citep{oliveira2013}.
Moreover there's no limitation on the amount of point sources.
The number of sources can either be equal, less or more than the number of
observation points, leading to well, under or overdetermined linear problem,
respectively.

@@

% EQL implementation on Harmonica.

@@

>>>>

The fundamental solution of any harmonic field can be obtained as follows
\citep[p.~37]{blakely1995}:

@@

Worth noting that solving equations~\ref{eq:linear-problem-g}
and~\ref{eq:linear-problem} is equivalent to performing an inversion and thus
solving an ill-posed problem by nature due to the non-uniqueness and the
instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions
(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
Worth noting that the number of sources can either be equal, greater or lower
than the number of observation points, leading to well, under or overdetermined
linear problem, respectively.

@@

@@

% Worth noting that the \emph{source below data} generates a number of sources
% equal to the data points, obtaining a well determined linear problem.
% The \emph{block averaged sources} layouts can generate a number of point
% sources equal or lower than the number of data points, well or
% overdetermined.
% The \emph{grid sources} is the only layout that can generate either a well,
% over or under determined problem.
